30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-13 paper.tex
Vulnerabilities, Sybil attack

	\subsection{NISAN}
		NISAN, or Network Information Service for Anonymization Networks \cite{panchenko2006nisan}, is an anonymization network which implements a distributed node discovery. Not only does a central node administrator (the Directory Server in Tor) imply trust in those servers, Panchenko et al. also argue that a central node administration (the Directory Server in Tor) does not scale, as the current directory server protocol was already improved two times to reduce bandwidth costs, with a fairly low amount of users.

		NISAN implements a DHT-based approach (Kademlia) for distributing node information, in such a way that does not require the client to know about all the nodes in the network (such as in Tor). To build a circuit, NISAN generates random IDs and searches for the closest hit throughout the network. This makes it possible to build a path with nodes picked in a random, uniform way among all nodes, without the trust of a third party.

		This does not fully protect against fingerprinting or bridging attacks (passive attacks), and suggest to do random walks throughout the network to mitigate that. The authors admit however this decreases the protection against an active attack.

@@

	\subsection{Sybil attacks}
		Hier wat over sybil attacks

>>>>

	\subsection{NISAN}
		Information about NISAN.

@@

	\subsection{Sybil attacks}
		The Sybil attack is an attack where a single attacker represents itself as multiple nodes in a peer-to-peer system. Abusing this, the attacker is able to propagate false assumptions about the network to other nodes.

		First described by Douceur, he \cite{douceur2002sybil} mathematically proves that this attack is always possible without a central authority that certifies the participating nodes in one way or the other, except under what he call "extreme and unrealistic assumptions of resource parity and coordination among entities", or in other words: require all participants to do something expensive (in terms of resources) to identify itself. This must be done within a small enough time frame that an attacker can't do this in sequence, but all nodes must do them in parallel.

		A fully distributed network that implements such a solution is the Bitcoin network [BITCOIN PAPER: http://s.kwma.kr/pdf/Bitcoin/bitcoin.pdf], in which computing power, and not the number of nodes is important for the general network consensus.
